Simple SIR

### 2018-05-22 Manuscript_figures_2017_12_12.Rmd
Updated figure numbering

#imp_logit$SD<-rep(0.005, times=nrow(imp_logit))
A<-ggplot(imp_logit, aes(x=reorder(X, X.IncMSE), y=X.IncMSE)) + 
    geom_bar(position=position_dodge(), stat="identity",
             colour="black", # Use black outlines,
             size=.3) +      # Thinner lines
    geom_errorbar(aes(ymin=X.IncMSE-SD, ymax=X.IncMSE+SD),
                  size=.3,    # Thinner lines
                  width=.2,
                  position=position_dodge(.9)) +
    scale_x_discrete(element_blank(), labels = c("rec_rate" = expression(gamma),
    "beta1" =  expression(beta[1]),"beta2" = expression(beta[2]), "beta3" = expression(beta[3]),
    "percep" = "r", "density"="d")) +
     ylab("Mean Decrease in Accuracy (%IncMSE)") +
    #ylab("")+
    theme_bw()+ theme(plot.margin = unit(c(0.1, 0, 0, 0), "cm"))+
    #ggtitle("(A)") + #" Variable Importance for Epidemic \nSuccess") +
    theme(axis.text=element_text(size=6), plot.title = element_text(size = 8), axis.title=element_text(size=6)) 
    #theme(plot.margin=unit(c(0.1,0.1,0,0), "cm"))
    # theme_bw(axis.text=element_text(size=14),    axis.title=element_text(size=14,face="bold"), plot.title = element_text(size = 40))
A

@@

## Supplementary Figure S1
Box plot of percep vs. rec rate vs. density for every RSF combination
```{r}
sub_data<-merged_data[which(merged_data$max_I>1),]
sub_data25<-sub_data[which(sub_data$density==0.25),]
sub_data50<-sub_data[which(sub_data$density==0.5),]

@@

## Supplementary Figure S2 (Heat maps, density=0.25)
Heatmap of max prevelance and mean duration for conspecific density=0.25 and comparing recovery rates of 0.1, 0.2, and 0.4
```{r}
r2<-merged_data[which(merged_data$rec_rate==0.2 & merged_data$density==0.25),]

@@

## Supplementary Figure S3 (Heat maps, density=0.5)
Heatmap of max prevelance and mean duration for conspecific density=0.5 and comparing recovery rates of 0.1, 0.2, and 0.4
```{r}
r2<-merged_data[which(merged_data$rec_rate==0.2 & merged_data$density==0.5),]

@@

## Figure S4
```{r}
#percep=3, rec_rate=0.2, density=0.5
p3r0.2d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.2 & merged_data$density==0.5),]
ii<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=max_prevalence, fill=as.factor(beta2)))
ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence", title="(A)", fill= expression(beta[2]))
ii<- ii+ theme(plot.title = element_text(size=7))
ii<- ii+ theme(axis.title = element_text(size=6))
ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=6))
ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
ii<- ii + theme(strip.text = element_text(vjust=0.5, size=6)) 
ii<- ii + theme(legend.text = element_text(vjust=0.5, size=6), legend.title=element_text(vjust=0.5, size=7))
ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
ii<- ii + theme(plot.margin=unit(c(0.1,0.1,0,0.1), "cm"))
ii

@@

tiff("FigureS4.tiff", height = 22.5, width = 17.8, units = "cm", compression = "lzw", res = 900)
multiplot(ii,jj, cols=1)
dev.off()
```

##Figure S4 (log version)
```{r}
#percep=3, rec_rate=0.2, density=0.5
p3r0.2d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.2 & merged_data$density==0.5),]
ii<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=log(max_prevalence), fill=as.factor(beta2)))
ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "ln(Maximum prevalence)", title="(A)", fill= expression(beta[2]))
ii<- ii+ theme(plot.title = element_text(size=7))
ii<- ii+ theme(axis.title = element_text(size=6))
ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=6))
ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
ii<- ii + theme(strip.text = element_text(vjust=0.5, size=6)) 
ii<- ii + theme(legend.text = element_text(vjust=0.5, size=6), legend.title=element_text(vjust=0.5, size=7))
ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
jj<- jj + theme(plot.margin=unit(c(0.1,0.1,0,0.1), "cm"))
ii

@@

tiff("FigS4_log.tiff", height = 11.5, width = 14, units = "in", compression = "lzw", res = 300)
multiplot(ii,jj, cols=1)
dev.off()
```

## Fig. S5
Comparing effects on landscape structure for a single RSF(\beta_1=6, \beta_2=2, \beta_3=-0.5) for different densities, perceptual distances, and recovery rates.
```{r}
#sub_data<-merged_data[which(merged_data$max_I>1),]
sub_data<-merged_data

@@

tiff("FigureS5.tiff", height = 22, width = 17.8, units = "cm", compression = "lzw", res = 1200)
multiplot(kk,mm,gg,hh,ii,jj, cols=2)
dev.off()

@@

## Supplementary Figure S6
See SimpleSIR.Rmd

##Supplementary Figure S7: Calibrating beta2/beta3 for RSF
```{r}
#Function to calculate rsf
myrsf=function(x,b1,b2) exp(x*b1+x^2*b2)   #caclulate rsf

@@

## Figure S8
Representation of neutral landscapes used for simulation studies
```{r}
#' Create neutral landscape maps
library(raster)

@@

#Now make the map
tiff("FigureS7_p_vs_H.tif", height = 8.7, width = 8.7, units = "cm", compression = "lzw", res = 900)
ggplot(data=df, aes(y=y, x=x)) +
  geom_raster(aes(fill=layer)) +
    theme_bw() +
  coord_equal() +
  facet_grid(p~ H) +
  #scale_fill_viridis(name="Resource quality")+
  #scale_fill_continuous(colours=c("#0000FFFF","#FFFFFFFF"))+
  scale_fill_gradient(low="lightgrey", high="darkgreen", guide=FALSE) +
  #scale_fill_continuous(guide = FALSE) +
  labs(y=my_y_title, x=my_x_title)+
  theme(axis.ticks = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())+
  theme(axis.title = element_text(size=10)) +
  theme(strip.text = element_text(vjust=0.5, size=9))+ 
  theme(legend.text = element_text(vjust=0.5, size=9), legend.title=element_text(vjust=0.5, size=10))
dev.off()

@@

## Figure S9
Random forest variable importance results from `party` package using cforest function
```{r}
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Random Forest Party Package May 2018")

setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures May 2018")
tiff("FigureS9_party.tiff", height =4.5, width =8.7, units = "cm", compression = "lzw", res = 1200)
#multiplot(A, B, C, cols=3)
prow
dev.off()

>>>>

#imp_logit$SD<-rep(0.005, times=nrow(imp_logit))
A<-ggplot(imp_logit, aes(x=reorder(X, X.IncMSE), y=X.IncMSE)) + 
    geom_bar(position=position_dodge(), stat="identity",
             colour="black", # Use black outlines,
             size=.3) +      # Thinner lines
    geom_errorbar(aes(ymin=X.IncMSE-SD, ymax=X.IncMSE+SD),
                  size=.3,    # Thinner lines
                  width=.2,
                  position=position_dodge(.9)) +
    scale_x_discrete(element_blank(), labels = c("rec_rate" = expression(gamma),
    "beta1" =  expression(beta[1]),"beta2" = expression(beta[2]), "beta3" = expression(beta[3]),
    "percep" = "r", "density"="d")) +
     ylab("Mean Decrease in Accuracy") +
    #ylab("")+
    theme_bw()+ theme(plot.margin = unit(c(0.1, 0, 0, 0), "cm"))+
    #ggtitle("(A)") + #" Variable Importance for Epidemic \nSuccess") +
    theme(axis.text=element_text(size=6), plot.title = element_text(size = 8), axis.title=element_text(size=6)) 
    #theme(plot.margin=unit(c(0.1,0.1,0,0), "cm"))
    # theme_bw(axis.text=element_text(size=14),    axis.title=element_text(size=14,face="bold"), plot.title = element_text(size = 40))
A

@@

## Figure S1
Random forest variable importance results from `party` package using cforest function
```{r}
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Random Forest Party Package May 2018")

setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures May 2018")
tiff("FigureS1_party.tiff", height =4.5, width =8.7, units = "cm", compression = "lzw", res = 1200)
#multiplot(A, B, C, cols=3)
prow
dev.off()

## Supplementary Figure S2
Box plot of percep vs. rec rate vs. density for every RSF combination
```{r}
sub_data<-merged_data[which(merged_data$max_I>1),]
sub_data25<-sub_data[which(sub_data$density==0.25),]
sub_data50<-sub_data[which(sub_data$density==0.5),]

@@

## Supplementary Figure S3 (Heat maps, density=0.25)
Heatmap of max prevelance and mean duration for conspecific density=0.25 and comparing recovery rates of 0.1, 0.2, and 0.4
```{r}
r2<-merged_data[which(merged_data$rec_rate==0.2 & merged_data$density==0.25),]

@@

## Supplementary Figure S4 (Heat maps, density=0.5)
Heatmap of max prevelance and mean duration for conspecific density=0.5 and comparing recovery rates of 0.1, 0.2, and 0.4
```{r}
r2<-merged_data[which(merged_data$rec_rate==0.2 & merged_data$density==0.5),]

@@

## Figure S5
```{r}
#percep=3, rec_rate=0.2, density=0.5
p3r0.2d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.2 & merged_data$density==0.5),]
ii<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=max_prevalence, fill=as.factor(beta2)))
ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence", title="(A)", fill= expression(beta[2]))
ii<- ii+ theme(plot.title = element_text(size=7))
ii<- ii+ theme(axis.title = element_text(size=6))
ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=6))
ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
ii<- ii + theme(strip.text = element_text(vjust=0.5, size=6)) 
ii<- ii + theme(legend.text = element_text(vjust=0.5, size=6), legend.title=element_text(vjust=0.5, size=7))
ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
ii<- ii + theme(plot.margin=unit(c(0.1,0.1,0,0.1), "cm"))
ii

@@

tiff("FigureS5.tiff", height = 22.5, width = 17.8, units = "cm", compression = "lzw", res = 900)
multiplot(ii,jj, cols=1)
dev.off()
```

##Figure S5 (log version)
```{r}
#percep=3, rec_rate=0.2, density=0.5
p3r0.2d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.2 & merged_data$density==0.5),]
ii<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=log(max_prevalence), fill=as.factor(beta2)))
ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "ln(Maximum prevalence)", title="(A)", fill= expression(beta[2]))
ii<- ii+ theme(plot.title = element_text(size=7))
ii<- ii+ theme(axis.title = element_text(size=6))
ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=6))
ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
ii<- ii + theme(strip.text = element_text(vjust=0.5, size=6)) 
ii<- ii + theme(legend.text = element_text(vjust=0.5, size=6), legend.title=element_text(vjust=0.5, size=7))
ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
jj<- jj + theme(plot.margin=unit(c(0.1,0.1,0,0.1), "cm"))
ii

@@

tiff("FigS5_log.tiff", height = 11.5, width = 14, units = "in", compression = "lzw", res = 300)
multiplot(ii,jj, cols=1)
dev.off()
```

## Fig. S6
Comparing effects on landscape structure for a single RSF(\beta_1=6, \beta_2=2, \beta_3=-0.5) for different densities, perceptual distances, and recovery rates.
```{r}
#sub_data<-merged_data[which(merged_data$max_I>1),]
sub_data<-merged_data

@@

tiff("FigureS6.tiff", height = 22, width = 17.8, units = "cm", compression = "lzw", res = 1200)
multiplot(kk,mm,gg,hh,ii,jj, cols=2)
dev.off()

@@

## Supplementary Figure S7
See SimpleSIR.Rmd

##Supplementary Figure S8: Calibrating beta2/beta3 for RSF
```{r}
#Function to calculate rsf
myrsf=function(x,b1,b2) exp(x*b1+x^2*b2)   #caclulate rsf

@@

## Figure S9
Representation of neutral landscapes used for simulation studies
```{r}
#' Create neutral landscape maps
library(raster)

@@

#Now make the map
tiff("FigureS9_p_vs_H.tif", height = 8.7, width = 8.7, units = "cm", compression = "lzw", res = 900)
ggplot(data=df, aes(y=y, x=x)) +
  geom_raster(aes(fill=layer)) +
    theme_bw() +
  coord_equal() +
  facet_grid(p~ H) +
  #scale_fill_viridis(name="Resource quality")+
  #scale_fill_continuous(colours=c("#0000FFFF","#FFFFFFFF"))+
  scale_fill_gradient(low="lightgrey", high="darkgreen", guide=FALSE) +
  #scale_fill_continuous(guide = FALSE) +
  labs(y=my_y_title, x=my_x_title)+
  theme(axis.ticks = element_blank(), axis.text.x = element_blank(), axis.text.y = element_blank())+
  theme(axis.title = element_text(size=10)) +
  theme(strip.text = element_text(vjust=0.5, size=9))+ 
  theme(legend.text = element_text(vjust=0.5, size=9), legend.title=element_text(vjust=0.5, size=10))
dev.off()

@@

### 2018-05-22 SimpleSIR.Rmd
Updated figure numbering

setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
tiff("FigureS6.tiff", height = 17, width = 17,8, units = "cm", compression = "lzw", res = 1200)
p
#multiplot(hh,ii, cols=1)
dev.off()
```

>>>>

setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
tiff("FigureS7.tiff", height = 17, width = 17,8, units = "cm", compression = "lzw", res = 1200)
p
#multiplot(hh,ii, cols=1)
dev.off()
```
